Visualizing probability distributions across bivariate cyclic temporal granularities

### 2021-05-16 main.Rmd
example of quasi rephrased - within each granule not period

With two linear granularities $G$ and $H$, if $G$ *groups into* or *finer than* $H$ then $G$ is of lower order than $H$. For example, if the bottom granularity is hour, then granularity day will have lower order than week since each day consist of fewer hours than each week.

@@

For example, day-of-year is quasi-periodic with either 365 or 366 granules of $B$ (days) within each period of $G'$ (years). The pattern repeats every $4$ years (ignoring leap seconds). Hence $R'= 4$. $Q_{B, G'}$ is a repetitive categorization of time, similar to circular granularities, except that the number of granules of $B$ is not the same across different granules of $G'$.

>>>>

With two linear granularities $G$ and $H$, if $G$ *groups into* or *finer than* $H$ then $G$ is of lower order than $H$. For example, if the bottom granularity is hour, then granularity $day$ will have lower order than $week$ since each day consist of fewer hours than each week.

@@

For example, day-of-year is quasi-periodic with either 365 or 366 granules of $B$ (days) within each granule of $G'$ (years). The pattern repeats every $4$ years (ignoring leap seconds). Hence $R'= 4$. $Q_{B, G'}$ is a repetitive categorization of time, similar to circular granularities, except that the number of granules of $B$ is not the same across different granules of $G'$.
